---
title: "Lab 02"
author: "Jason Gerber"
date: "2/1/2021"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    number_sections: no
    toc_float: yes
    df_print: paged
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```

## Shell commands

In this repo is a zip file named `organize_me.zip`. It can by unzipped by
running R code `unzip("organize_me.zip")`. Do this in your console so you only 
unzip the folder once and not each time you knit the Rmd file.

The files in `organize_me/` contain a sample of various files you may have if 
you run a simulation on a high performance computer. Organize the contents in
`organize_me/` using the terminal and shell according to the following steps.

1. delete all `.input2` files;
2. remove the `flags/` directory and all of its contents;
3. place the test data text files in a directory named `test_data/`;
4. place the `.sh` files in a directory named `scripts_shell/`;
5. place the `.R` files in a directory named `scripts_R/`;
6. place the `.qsub` files in a directory named `hpc_start/`;
7. copy directory `organize_me/` and name the copy `simulations/`;
8. delete directory `organize_me/` and all of its contents.



## Attributes

Create a date-time object based on the atomic double vector below. You'll
need to set the class attribute to `"POSIXct"`

```{r}
z <- seq(0, 3600 * 10, by = 3600)

as.Date.POSIXct(z)
```

What do you notice about the date-time? If you are unsure, check out
[Unix Epoch](https://en.wikipedia.org/wiki/Unix_time). A time converter is
available [here](https://www.epochconverter.com).



## Subsetting

Consider the atomic vector `x`.

```{r}
set.seed(0826) # set seed to ensure reproducibility
x <- sample(x = c(letters, -15:15), size = 50, replace = TRUE)
x
```

Complete the following without using any loops.

1. Subset only the letters from `x`.

```{r}
x[is.na(as.numeric(x))]

```

2. Subset only the negative numbers from `x`.

```{r}
x <- x[!is.na(as.numeric(x))]
x[x<0]
```

3. Select the numbers divisible by 3 from `x`.

```{r}
x <- x[!is.na(as.numeric(x))]
x <- as.numeric(x)
x[(x %% 3) == 0]


```

4. Remove all values with an even index from `x`.

```{r}
x[-seq(2, length(x), 2)]



```



## Git from the command line

[Git cheat sheet](https://www.atlassian.com/git/tutorials/atlassian-git-cheatsheet)

1. Assuming you completed the shell commands tasks above, use git from the 
   command line to stage and commit your work. 

2. After committing, delete directory `simulations/`.

3. Use git from the command line to stage and commit your work. 

4. Use git from the command line to revert your last commit in order to 
   recover `simulations/`. Refer to the above cheat sheet for assistance.
